Additional analysis

### 2020-01-24 analysis/03_additional-analysis.Rmd
Remove this balance section bc it's in 02_analysis already
Export collapsing variable table

# Balance

```{r}

```

@@

collapsed_likelihood %>% 
  pandoc.table(justify = "ll")
```

@@

```{r collapsed-probit, warning=FALSE, message=FALSE, results="hide", cache=TRUE}
collapsed_oprobit <- stan_polr(donate_likely ~ crackdown, data = results,
                               prior = R2(0.25, what = "mean"), prior_counts = dirichlet(1),
                               method = "probit")
```

>>>>

@@

collapsed_likelihood %>% 
  pandoc.table.return(justify = "ll") %T>%
  cat(file = here("analysis", "output", "tables", "tbl-collapsed-likelihood.md")) %>% 
  cat()
```

@@

```{r collapsed-probit, warning=FALSE, message=FALSE, results="hide", cache=TRUE}
collapsed_oprobit <- stan_polr(donate_likely ~ crackdown, data = results,
                               prior = R2(0.25, what = "mean"), prior_counts = dirichlet(1),
                               method = "probit",
                               chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
```
